---
title: "UCI Explorative Data Analysis"
author: "Masud Afschar"
date: "6/7/2020"
output: html_document
---

First, we combine all available data into one single data set:

```{r}
data.cleveland <- as.data.frame(read_table2('datasets/processed.cleveland.csv', na = "?"))
names(data.cleveland)[names(data.cleveland) == "num"] <- "class"
data.va<- as.data.frame(read_csv('datasets/processed.va.csv', na = "?"))
data.switzerland <- as.data.frame(read_csv('datasets/processed.switzerland.csv', na = "?"))
data.hungarian <- as.data.frame(read_table2('datasets/processed.hungarian.csv', na = "?"))

data <- rbind(data.cleveland, data.va, data.switzerland, data.hungarian)
```

Next, we should check the content:

```{r}
summary(data)
```

We see that the data needs some cleanup. There are a lot of missing values in the `ca` and `thal` columns. Further, we can see that there are values of 0 for `chol`, which is clinically not plausible. These values need to be replaced with NAs as well.

```{r}
data$chol[data$chol == 0] <- NA
summary(data)
```

We saw that the class labels are heavily imbalanced. This will very likely result in a poor prediction model. Thus, we will condense the labels two only two classes: 0 for no heart disease and 1 for heart disease.

```{r}
data$class[data$class == 2 | data$class == 3 | data$class == 4 ] <- 1
summary(data)
```

This data set is more or less alright for model building and will be saved.

```{r}
write.csv(data, "datasets/processed.concat.csv", row.names = FALSE)
```




